%------------------------------------------------- ------------------------------
% SECTION TITLE
%------------------------------------------------- ------------------------------
\cvsection{Open Source}


%------------------------------------------------- ------------------------------
% CONTENT
%------------------------------------------------- ------------------------------
\begin{cventries}

%------------------------------------------------- --------

\cventry
     {opensumi is a framework developed by Ali and Ant to help developers quickly build local and cloud IDEs. \href{https://github.com/opensumi/core}{https://github.com/opensumi/core}} % subtitle
     {OpenSumi collaborative editing module} % title
     {} % Location
     {2022.07 - 2022.08} % Date(s)
     {
       \begin{cvitems} % Description(s) of tasks/responsibilities
         \item {2022 \textbf{Alibaba Summer of Code} subject}
         \item {The module developed this time roughly realizes the basic editor \textbf{real-time collaboration} function. }
         \item {Understand the basic architecture design and underlying technologies required by editors such as vscode / \textbf{IDE}, such as dependency injection, websocket, IPC/RPC, etc. }
         \item {Learn about other work in the complete project besides development, such as CI/CD, unit testing, coding/commit specification, teamwork communication, etc. }
         \item {Become a \textbf{member} of this community, and learn more about the application of \textbf{object-oriented programming} in real projects. }
       \end{cvitems}
     }

%------------------------------------------------- --------

\cventry
     {Logseq is an open source knowledge management application that supports block-level bidirectional links. \href{https://github.com/logseq/logseq}{https://github.com/logseq/logseq}} % Subtitle
     {Logseq Active Contributor} % Title
     {} % Location
     {2022.12 - now} % Date(s)
     {
       \begin{cvitems} % Description(s) of tasks/responsibilities
         \item {The project is mainly developed using \textbf{React}, Tailwind CSS, ClojureScript, JavaScript, DataScript, Electron. }
         \item{As a daily user of the app, dissatisfied with the existing experience. Reported numerous bugs and fixed them. Mainly related to \textbf{editor, Electron} etc. }
         \item {Several features are proposed and implemented, such as support for pasting in multiple formats, and a convenient \textbf{clipboard data viewing tool}. }
         \item{Write E2E tests for this item. Responsible for maintaining the issues area of the project in spare time. }
         \item{Improved the \textbf{user experience} of the app and learned more about the application of \textbf{functional programming} in real projects. }
       \end{cvitems}
     }

%------------------------------------------------- --------
\end{cventries}